Lab journal

### 2024-10-02 index.Rmd
indexupdate

# First page of something totally awesome yes.

@@

------------------------------------------------------------------------

```{=html}
<!--- The ---- is a visual line (page break looking mf) on the 
website 
Always ADD A SPACE BETWEEN A PAGE BREAK AND the next comment, otherwise it will appear on page --->
```
```{=html}
<!--- This is the best way to write a comment. 
It also demonstrates, you can add html directly in your rmarkdown file. See: https://www.w3schools.com/html/html_comments.asp --->
```
```{=html}
<!--- to use a multi column page we use Pandoc's fenced Div. 
see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html 
But please note, we are not here to make a beautiful website, our intention is just to have a quick lab journal up and running --->
```
::: columns
::: {.column width="50%"}
# Lab Journal

@@

<br>

------------------------------------------------------------------------

## Open Science

>>>>

::: columns
::: {.column width="50%"}
# First page of something totally awesome yes.

@@

@@

```{=html}
<!--- The ---- is a visual line (page break looking mf) on the 
website 
Always ADD A SPACE BETWEEN A PAGE BREAK AND the next comment, otherwise it will appear on page --->
```
```{=html}
<!--- This is the best way to write a comment. 
It also demonstrates, you can add html directly in your rmarkdown file. See: https://www.w3schools.com/html/html_comments.asp --->
```
```{=html}
<!--- to use a multi column page we use Pandoc's fenced Div. 
see here: https://bookdown.org/yihui/rmarkdown-cookbook/multi-column.html 
But please note, we are not here to make a beautiful website, our intention is just to have a quick lab journal up and running --->
```
## Open Science
